An Innovative Storage Stack Addressing Extreme Scale Platforms and Big Data Applications

### 2014-05-12 paper.tex
new Buffy machine specs.
finished adding the machine specs

\begin{figure}[htbp]
\vspace{-0.10in}
\centering
\includegraphics[width=\columnwidth]{images/vol-arch.png}
\vspace{-0.10in}
\caption{Architectural view of the VOL abstraction mechanism}
\label{fig:vol-arch}
\vspace{-0.10in}
\end{figure}

@@

Since HDF5 has traditionally offered an interface focused on files and the
internal data types, such as datasets, these concepts must be mapped onto the
proposed FFSIO data storage concepts. This mapping is shown in Table~\ref{tab:mapping}

\begin{table}[ht]
    \vspace{-0.10in}
    \centering
    \caption[HDF5 to FFSIO Mapping]{HDF5 Data Model to FFSIO Data Model Mapping}
    \bigskip
    \vspace{-0.15in}

    \begin{tabular}{|r|r|}
\hline
HDF5 & FFSIO\\
\hline
file & container \\
dataset & array \\
group & key-value store \\
attribute(s) & key-value store \\
\hline
    \end{tabular}
    \label{tab:mapping}
\end{table}

In Section~\ref{sec:iod} below, the FFSIO types are described in more detail.

@@

All of the tests are performed on the Buffy Cray test cluster at Los Alamos
National Laboratory. It consists of 84 nodes each with dual, 8 core Intel
Xeon ES-2670 CPUs at 2.6 GHz and 32 GB RAM. The interconnect is Cray Gemini.
The storage array are three sets of SSD-based Lustre file systems.

>>>>

\begin{figure}[htbp]
\vspace{-0.10in}
\centering
\includegraphics[width=\columnwidth]{images/vol-arch.png}
\vspace{-0.20in}
\caption{Architectural view of the VOL abstraction mechanism}
\label{fig:vol-arch}
\vspace{-0.10in}
\end{figure}

@@

Since HDF5 has traditionally offered an interface focused on files and the
internal data types, such as datasets, these concepts must be mapped onto the
proposed FFSIO data storage concepts. At a high level, think of the HDF5 types
mapping to FFSIO types as follows: file $\rightarrow$ container, dataset $\rightarrow$
array, and groups and attributes $\rightarrow$ key-value store.
%This mapping is shown in Table~\ref{tab:mapping}

%\begin{table}[ht]
%    \vspace{-0.10in}
%    \centering
%    \caption[HDF5 to FFSIO Mapping]{HDF5 Data Model to FFSIO Data Model Mapping}
%    \bigskip
%    \vspace{-0.15in}
%
%    \begin{tabular}{|r|r|}
%\hline
%HDF5 & FFSIO\\
%\hline
%file & container \\
%dataset & array \\
%group & key-value store \\
%attribute(s) & key-value store \\
%\hline
%    \end{tabular}
%    \label{tab:mapping}
%\end{table}
%
In Section~\ref{sec:iod} below, the FFSIO types are described in more detail.

@@

All of the tests are performed on the Buffy Cray XC30-AC at LANL.  It consists
of 64 compute nodes each with dual, 8 core Intel Xeon ES-2670 CPUs at 2.6 GHz
and 64 GB RAM.  The interconnect is Cray Aries. There are 14 IO nodes
consisting of single socket, 8 core Intel Xeon ES-2670 CPUs at 2.6 GHz with 32
GB of RAM.  There are also a metadata, login, and 2 boot nodes.  The storage
array has disk and SSD paritions. One is a DDN Lustre system with 192 TB disk
usable with a minimum of 5 GB/sec performance. The rest are SSDs consisting of
an EMC flash array connected via FDR InfiniBand with 22 TB and 48 GB/sec write
performance.
